Toward theories of deliberated preferences

### 2020-12-08 simple.tex
Reused § about need for adaptive argumentation strategies

	This example thus defines a theory that anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar_\text{non-linear}$ as an alternative argument in case $\ar_\text{for$P$}$ does not convince an individual.
\end{example}
Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.

@@

\end{example}

>>>>

	This example thus defines a theory that anticipates a possible attack using $\ar_0$ against $\ar_\text{for$P$}$, and prepares $\ar_\text{non-linear}$ as an alternative argument in case $\ar_\text{for$P$}$ does not convince an individual.
\end{example}

Importantly, theories of \ac{DJ} must also be able to argue differently for different individuals. Even considering individuals with the same \ac{DJ}, different individuals might consider as decisive different arguments. Accepting non trivial propositions often requires to accept several sub-propositions, that together permit to be convinced of the acceptability of the proposition. Depending on which of these sub-propositions the individual already considers to be acceptable, parts of the argumentation can be omitted, and, perhaps, must be omitted: an overly long argument, stating many things that the listener already knows, has fewer chance to convince the listener than a short argument that goes straight to the point about which the listener doubts. 
%Mathematicians do not write their proofs starting from the axioms of set theory: they use results that they assume the reader already is aware of, and are ready (in principle) to supply the proofs of these intermediate results if a reader has doubt about some of them. 
In other words, what is needed for a theory of \ac{DJ} is not just a capacity to produce a unique decisive argument, with the claim that this argument will convince individuals in $I$, but rather a capacity to produce dynamically arguments that depend on which counter-arguments the individual finds appealing, with a claim that this dynamic argumentation strategy will succeed in convincing individuals in $I$.

@@

\end{example}
Refining such descriptive theories to let them articulate better the arguments and counter-arguments, and describing more realistic argumentative strategies, is left for future work.
